Tool-driven Revolutions in Archaeological Science

### 2018-12-07 analysis/paper/jcaa-paper.Rmd
try to make plot-legend in "articles per year citing R in top ecology journals" readable by extending the x-Axis.
still a line break in preoceedings of the royal society. -.-

```{r ecology-articles-citing-r-plot, fig.cap=str_glue('Articles per year citing R in top Ecology journals ({prettyNum(articles_shown_in_plot,",")} articles out of {prettyNum(how_many_articles_in_top_journals_for_cran_cites,",")}). Data from Web of Science for 2007-2017')}
min_y <- 2007
max_y <- 2025
all_sciences_citing_R_over_time <- 
ggplot(cran_cites_all_areas_top_journals_by_year,
       aes(PY,
           prop,
           colour = SO)) +
  geom_line(size = 2) +
  geom_text_repel(
    data = subset(cran_cites_all_areas_top_journals_by_year, 
                  PY == max(PY)),
    aes(label = str_wrap(SO_n, 40)),
    size = 4,
    nudge_x = 0,
    hjust = 0,
    segment.color = NA,
    direction = "y"
  ) +
   scale_x_continuous(breaks = min_y:max_y,
                     labels = c(min_y:2017, rep("", length(2018:max_y))),
                     limits = c(min_y, max_y)) +
#  scale_y_continuous(labels = scales::percent) +
  xlab("Publication year") +
  ylab("Number of Articles in that journal in that year") +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

@@

min_y <- 2007
max_y <- 2040

all_archaeology_citing_R_over_time <- 
ggplot(archy_cran_cites_all_areas_top_journals_by_year,
       aes(PY,
           prop,
           colour = SO)) +
  geom_line(size = 2) +
  geom_point() +
  geom_text_repel(
    data = archy_cran_cites_all_areas_top_journals_by_year %>% 
      group_by(SO) %>% 
      slice(which.max(PY)) , 
    aes(label = SO_n),
    direction = "y",
    size = 5,
    nudge_x = 1,
    hjust = 0) +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5)) +
  scale_x_continuous(breaks = min_y:max_y,
                     labels = c(min_y:2017, 
                                rep("",
                                    length(2018:max_y))),
                     limits = c(min_y, max_y)) +
  #scale_y_continuous(labels = scales::percent,
   #                  limits = c(0, 0.2)) +
  xlab("Publication year") +
  ylab("Number of articles in that journal")

@@

# combine main plot and subplot
all_archaeology_citing_R_over_time_and_subplot <- 
all_archaeology_citing_R_over_time  +
  annotation_custom(grob = ggplotGrob(jas_cites_r), 
                          xmin = 2030, xmax = 2040, 
                          ymin = 12, ymax = 17) # changed position because of numbers now instead of percentage

>>>>

```{r ecology-articles-citing-r-plot, fig.cap=str_glue('Articles per year citing R in top Ecology journals ({prettyNum(articles_shown_in_plot,",")} articles out of {prettyNum(how_many_articles_in_top_journals_for_cran_cites,",")}). Data from Web of Science for 2007-2017')}
min_y <- 2007
max_y <- 2050
all_sciences_citing_R_over_time <- 
ggplot(cran_cites_all_areas_top_journals_by_year,
       aes(PY,
           prop,
           colour = SO)) +
  geom_line(size = 2) +
  geom_text_repel(
    data = subset(cran_cites_all_areas_top_journals_by_year, 
                  PY == max(PY)),
    aes(label = str_wrap(SO_n, 40)),
    size = 4,
    nudge_x = 0,
    hjust = 0,
    segment.color = NA,
    direction = "y"
  ) +
   scale_x_continuous(breaks = min_y:max_y,
                     labels = c(min_y:2017, rep("", length(2018:max_y))),
                     limits = c(min_y, max_y)) +
#  scale_y_continuous(labels = scales::percent) +
  xlab("Publication year") +
  ylab("Number of Articles in journal per year") +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

@@

min_y <- 2007
max_y <- 2050

all_archaeology_citing_R_over_time <- 
ggplot(archy_cran_cites_all_areas_top_journals_by_year,
       aes(PY,
           prop,
           colour = SO)) +
  geom_line(size = 2) +
  geom_point() +
  geom_text_repel(
    data = archy_cran_cites_all_areas_top_journals_by_year %>% 
      group_by(SO) %>% 
      slice(which.max(PY)) , 
    aes(label = SO_n),
    direction = "y",
    size = 5,
    nudge_x = 1,
    hjust = 0) +
  theme_minimal() +
  theme(legend.position="none",
        axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5)) +
  scale_x_continuous(breaks = min_y:max_y,
                     labels = c(min_y:2017, 
                                rep("",
                                    length(2018:max_y))),
                     limits = c(min_y, max_y)) +
  #scale_y_continuous(labels = scales::percent,
   #                  limits = c(0, 0.2)) +
  xlab("Publication year") +
  ylab("Number of Articles in journal per year")

@@

# combine main plot and subplot
all_archaeology_citing_R_over_time_and_subplot <- 
all_archaeology_citing_R_over_time  +
  annotation_custom(grob = ggplotGrob(jas_cites_r), 
                          xmin = 2030, xmax = 2045, 
                          ymin = 12, ymax = 17) # changed position because of numbers now instead of percentage
